---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LOVE

<!-- badges: start -->
<!-- badges: end -->

LOVE performs overlapping clustering of features under a structured latent 
factor model.

## Installation

You can install the released version of LOVE from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("LOVE")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("bingx1990/LOVE")
```
## Example

This is a basic example which shows you how to use two main functions of LoveER: 
LOVE and ER. We start by generating a synthetic data set. 

```{r data generating}
p <- 6
n <- 50
K <- 2
A <- rbind(c(1, 0), c(-1, 0), c(0, 1), c(0, 1), c(1/3, 2/3), c(1/2, -1/2))
Z <- matrix(rnorm(n * K, sd = 2), n, K)
E <- matrix(rnorm(n * p), n, p)
X <- Z %*% t(A) + E
```

The following code calls the LOVE function to perform overlapping clustering of 
the columns of the \strong{X} matrix.

```{r example-LOVE}
# library(LOVE)
# # basic example code
# res_LOVE <- LOVE(X)
# res_LOVE <- LOVE(X, pure_homo = T)
```



